Binning Strategies and Related Loss for Large Data

### 2015-03-01 Paper.Rnw
move 2 dimension extension discussion up and add description of linearization.  Note that I have adjusted the notation such that j indexes X, k indexes Y and l is the linearized index s.t. l=j+J(k-1)
oops new extension to 2d not saved before last push

\subsection{Standard Rectangular Binning Algorithm}
\hh{XXX Speed this discussion up a bit - you don't need to lay out what you will do in this section, just do it.}

@@

\subsection{Random Binning Algorithm}

@@

>>>>

The standard and random binning algorithms are easily extendable to higher dimension. For the purposes of creating binned scatterplots we will specify extension to rectangular binning in two dimensions. In this case we wish to assign data pairs $(x_i, y_i)$ to bin centers of the form $(x_j^\ast,y_k^\ast)$, with $j \in \{1,\dots,J\}$ and $k \in \{1,\dots,K\}$, where $J$ and $K$ are the number of bins in the X and Y dimensions, respectively. \ktm{The two ($j$,$k$) pairs that index the bin centers can be linearized to a single index such that $l = j + J(k-1)$; thus making $j$ the fast running index and $k$ the slow running index.  With this linearized index for all bins we now have a set of bin centers of the form $(x_l^\ast,y_l^\ast)$, with $l \in \{1,\dots,L\}$, where $L=J\dotK$.}

The standard rectangular binning function $b(.) : (x_i,y_i) \rightarrow (x^\ast_l,y^\ast_l)$ is defined as 
%
\begin{eqnarray}\label{standrecbin}
b(x_i,y_i) = (b_X(x_i),b_Y(y_i))
\end{eqnarray}
%
where $b_X(x_i)$ and $b_Y(y_i)$ are the univariate standard binning algorithms for the X and Y dimensions respectively. The random rectangular binning function, $b^r(\cdot): (x_i,y_i) \rightarrow (x^\ast_l,y^\ast_l)$ can similarly be defined as
%
\begin{eqnarray}\label{randrecbin}
b^r(x_i,y_i) = (b^r_X(x_i),b^r_Y(y_i))
\end{eqnarray}
%
where $b^r_X(x_i)$ and $b^r_Y(y_i)$ are univariate random binning algorithms for each dimension. Figure~\ref{fig:BinningTutorial} provides an illustration of each binning process extended to a two dimensional situation.

\subsection{Standard Rectangular Binning Algorithm (old - to be removed)}
\hh{XXX Speed this discussion up a bit - you don't need to lay out what you will do in this section, just do it.}

@@

\subsection{Random Binning Algorithm (old-to be removed)}

@@

\subsection{Extensions to Rectangular Binning (old-to be removed)}
